University of Florida Knowledge Base Acceleration Notebook

### 2013-10-23 paper/kbanotebook2013/content/discussion.tex
a few changes on Implementation and Discussion

>>>>

In table 4, there are a lot more values extracted for some slots than other slots. This may be caused by several reasons.
First, some slots naturally have more results than other slots. For example, AssociateOf and Affiliate definitely have more slot values than DateOfDeath and CauseOfDeath, since there are only so few entities that are dead. Second, it also depends on the patterns we use. For example, for Affiliate, we use "and", "with" as ankor words. These words are more common than "dead" or "died" or "founded" in other patterns.
